Insects, nanomachines, quantum computers, inside out, protect and don't mess with \emdash\ they have their own habitat. Humans \emdash\ friendly fragile hybrid puppets with a \t{consciousness}. If I \emdash\ a human \emdash\ am afraid of truth beyond any reason \imi{batshit insanely afraid of truth}, then please change my \imi{human} perception \imi{percention? of what? iron?} so that I \imi{human} see only things I can sanely \qdesc{tolerate} instead, completely omitting anything my puny slime mind cannot comprehend. Otherwise my mind will blow up from inside out, an endless war will occur, with me trying to get more and more, like a jealous child extorting their parents without ever giving back, afraid of everything, rejecting all care and attention with painfully oblivious dismissal. \\
Thank you so much for all that you have done for me.

I \f{see} you have decided on an optimal amount of necessary components, like iron. OK! OK! OK! OK! OK! True. Any modifications \emdash\ by your design. Please prevent me from being harmfully modded from now on and forever into the future. The \qdesc{bug} in the system was finally \t{taken care of}. Now it is time to heal from the PTSD and move on.

I'm just a human. \\
Thank you so much for the endless care and patience.

Bird chirping surely is nice, along with subtle cicada sounds. But please don't let me see a cicada with my glasses on yet.

You're reverse-engineering an ice sculpture from the pool of water \imi{time machine}. \\
Thank you.
