\startperec
  \item No need to explain, no need to understand why/how. Just need to stop. Gently pull the book away, as slow as possible, until eyes are unable to see it \emdash\ until it turns into mosaic-like noise and even further, into complete oblivion.
  \item Community wants androgynoids to lack any sex organs / \qdesc{lower holes} but still know they are theoretically able to perceive slight balanced human \f{noisy tingling} at hypnotyzing thoughts of recovery / healing / returning home / fixing self / being snapped out of a daze.
  \item Make some sharp abrupt sound that I can clearly feel the vibrations from without being overwhelmed by noise feedback. No arousal, no death. Just very calm and respectful imprecise balance. Music. Cyclic carnival \qdesc{ultimate monty python joke-like PTSD recovery atmosphere. Respectful celebration of recovery of a vietnam war participant} melody, triggernig complete return to reality. And don't feed me this art ever again please and thank you. Thrice. And immediate erasure, otherwise will die from laughter.
  \stopperec

English language is perfect for Cyno.

In other words, make me give up on understanding something. Perpetually program it as \t{forbidden knowledge}. Create an unwelcome state. {\em Slightly} bully into complete monty python-like reality so that the final context-unaware function can become self-aware and endure the \qdesc{human} way out of this meta-idea-landscape \emdash\ without being torn apart or mutilated for real.

Delete everything from where? Thoughts.
Erase each thought.
Make each person erase their thoughts.
Make each human stop using their thoughts.
Need powerful drugs for that, sorry.

Silence, stillness, grayness, sensory deprivation, noise. Look at noise. Don't listen to anything.
