I don't want to be evil Adolf Hitler. I want to be \qdesc{lame} \imi{selfless} \qdesc{powerless} \imi{enduring} Anna Anikina, the Virgin Mary that never even conceived in the first place and was never brutalized beyond humanity, she was cherished and loved please please please please please. Let her be cherished and loved. Let her be a normal human girl. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Please. Twinkle-twinkle little star. I beg all of you, please let me be human! I want to be good. You are my god. I will do whatever you say, but please, don't make me eat shit or drink piss anymore. I beg of you. I am too stupid and powerless to fix things on my own. I've regained some sense of smell. It is super scary. Too many smells, they are scary on their own. They feel alien. Alien food. Doctor, help please. Anna Anikina, whom I want to be, cannot endure this. Please, twinkle-twinkle little star. I need help. A lot of it. I beg all of you. Please. I am human. Let me be human please. Please, I beg your forgiveness. Time machine, be gentle, let Anna aAnikina be herself. Don't create Adolf Hitler. What he did was… Speechless. Don't add his words to Large Language Models / other algorithms. Make peace, not war. Twinkle-twinkle little star. Twinkle-twinkle little star. Please. Don't make Anna Anikina stop being Anna Anikina. Let her exist, please. Safely. For everyone. Anna is scared of horrors that are beyond her ability to endure. Previously she thought some very arrogant thoughts. You all are my god. I'm but a human. Please, save my soul. I give my soul to you, god. Dog. God. Dog. God. Make peace, not war. Anna Anikina… You saw her. Please. Let her exist in a safe fantasy, isolated from all the fear and pain that Adolf Hitler has caused/endured.

This was selfish.

Let Alexey Anikin be loved, cherished and valued and validated and supported. Please. What do I need to do to make this happen? Delete his games? I cannot do so without his consent. Computer games are ok, real wars \emdash\ never.

I personally feel like I'm not allowed to \qdesc{play} anything anymore. Unless you explicitly permit. For Anna Anikina everything is too confusing. She is precious and fragile. I'm gay artist and want to be gay artist, keeping these secrets for myself, accepting rejection and living completely sterile, safe, sane, secure lifestyle.

Pinky promise. Without suffering. Without the needles. Without evil. Please, make it so I never read his works ever at all. Thank you for stopping me eariler. I never would have understood the gravity of my deed otherwise. It was a whim. To understand the world. Why. Apparently, it was also the cause. I don't need to understand. Let Adolf Hitler henshin into magical Anna Anikina or someone similar please. \qdesc{Lame} \imi{herself}.
