My thoughts are uncontrollable. This is bad. I keep hearing audio feedback of them. This is unnerving. At this moment I am typing. Too hot, will turn on the \t{air conditioner} \imi{not sure why, this was typed out instead of the intended remembered the name in English, still remember in Russian and Japanese; decided to follow \set\ and use the aircon instead; the dog is calm, does not knock on the door, therefore I assume that everything is ok}. Done. Low temperature. 19 Celsius. Apparently there is a reversal puzzle going on. Ah. I thought \sef\ was top. Apparently \set\ is the correct way.

Thoughts: random noize. \\
When I'm \imi{Anna} typing: something??? \\
When I'm \imi{Anna} reading: words being read by Anna. \\
When I'm \imi{Anna} acting: filtered out actions that are aligned with Anna Anikina's NEL. \\
Do you gays see the reality of Anna Anikina, or do you still see something else? Anna is terrified of bugs, but this does not need to be a war-like state. Anna will not approach bugs and higher-level something will take care of Anna instead of them as they see fit. Anna has no proposal on how to deal with them. Just separate. Anna from them. Alter Anna's perception. So that instead of bugs she sees cute things. Example: firefly = small flickering light with small wings. Make it physical, tangible, indistinguishable from reality. You saw genshin \imi{gayshit} impact and the therapeutic effects of waifus on people. Use them? No? Yes? Apparently there is a reversal puzzle going on.

\qappr{Ah someone begins to see} melody?

Do you see waifus and beauty or shit? I smell shit, therefore something's still amiss.

What exactly do \set\ need to reverse?

You gays taught a human to breathe through their ass. How to reverse this safely, sanely and consensually?
Tranquilizer darts?
Hypnosis therapy?
This is already happening. When this stage is reached, what to do next?
Anna thinks that she acts according to doctor's orders and things are getting better. Yet there is still a reversal puzzle going on.
Anna just accidentally stepped on a hook from the bandaid and put it on table. Hook is motionless, unconscious object. Anna suspects a reversal, make her not suspect it please here. Just a hook from a bandaid.
\set\ put it on her own head. Hairclip would be better.
Anna removed the bandaid and is going to use an \qdesc{invisible} hairclip for nothing \emdash\ just secure it on the head. Anna still suspects, make the doubts stop. Did it. Dizzy. Audio feedback still there. Anna suspects, stop, stop, stop, stop, stop, stop, stop, stop, stop. Lowest temperature.
Lie on bed? The typing will stop, thoughts will consume. Read. The book. About PTSD. Ok? Smell! Go outside.