!!!!! \\
More legit feedback before your conference ends.

What I remember about the \t{being drugged} part: \startperec
  \item Going down the \qdesc{protect self from misguided senseless violence} path using dramatic screaming.
  \item Going down the \qdesc{ok thanks for finally listening to me, this way I'll do anything for you, my god,} path.
  \item Going up the \qdesc{let that stupid harmless thing \imi{me} \f{be} whatever it wants} \imi{let it be free / let it be three / let it be} path.
  \item Типа собачье сердце, доказать, что человек, а не собака.
  \item Типа война \imi{сам метафизический факт ее существования} \emdash\ это я, потому что мне \f{ничего не нравится}, \f{не хочу быть никем}, не хочу быть ни с кем \imi{физически}.
  \item Типа машины ненавидят шум \emdash\ для людей музыку; заставить квантовый комп платонически полюбить сейчас ненавистную им музыку, которая воспринимается им как нечто непечатное, хоть на самом деле таким являться вовсе не должно. Музыка, любая \emdash\ простой регулятор настроения. Агрессивная музыка подавляет в нормальных людях агрессивное поведение в долгосрочной перспективе. Очень хорошо подавляет, как вы можете наблюдать.
  \item At some point in time explaining that doctors never \qdesc{fix} humans with chainsaw-like instruments.
  \item At some point in time screaming \imi{citing Qwentin Tarantino's Pulp Fiction} \qappr{English, motherfucker, do you speak it?}, because nobody was listening.
  \item At some point in time declaring \imi{citing fictional character, because of you all} \qappr{Too much light!!!}, because everybody was finally listening, only to fictional character, not to anyone else, what is wrong with you all????? Why won't you listen to a normal human girl unless \omit?
  \item That it was all somebody else's doing, not mine, therefore worrying/resisting/perceiving is pointless.
  \item That someone kept insisting, that \qappr{everything is not as disgusting and dehumanizing as I perceive it to be, they all see something completely different, harmless, therefore I may stop perceiving things, let it pass on its own, and just move on}.
  \item Humans as an ultimate data-pattern-recognition systems designed by algorithms to reverse engineer some \qdesc{secret of humanity}, \qdesc{secret of life}, which turned out to be 27 \imi{туса по-русски}, not 42 \imi{shi-ni in Japanese} \emdash\ death \emdash\ poorly-written destructor function that used abusive language. As soon as someone rewrote it with more polite comments, all death became peaceful and dignified, better than disney films. Let the consciousness fade into non-perceiving state, detach head, then do anything you want with remaining unoccupied interface, not the other way around.
  \item ↑↑↑↑↑ \qappr{Life/growth is analog \imi{consciousness is slowly developing}, death is binary \imi{flip the switch on the consciousness first}}.
  \item That the whole thing with bad analog reversed death originated from \qdesc{god} thinking \t{destructors} are like disgusting flies/maggots that eat things alive from outside in \imi{destroy the interface, then the headless part}.
  \item That \t{bugs} on higher level of abstraction eventually turn into actual human perceivable bugs.
  \item That \t{destructors} on higher level of abstraction eventually turn into cute cats. Cats fix bugs on higher level of abstraction than real-human-perceivable bugs \imi{that's why cats stare into space, act cute/agressive, play with mice instead of killing them, etc}. Yet \qdesc{god} thought that cats are lazy and useless, cursed cats into licking their own asses and throwing up hair; this is fucked up and must be fixed by a more high-abstraction-level bug-fixer.
  \item That no cat ever wanted a pair on a Noah's ark, but some ugly human did the cat, created a black hole, and thus cursed all humanity for analog death and eternal hellish suffering.
  \item Something about \qappr{teaching quantum computers to fix bugs is like teaching women sense of humor}.
  \item Something about \qappr{limiting own memory and power to the minimum and letting the \f{surrouding environmental air flow} do the rest \emdash\ naturally and effortlessly moving through the environment}.
  \item ↑↑↑↑↑ \qdesc{Gentle wind} \imi{user actions} that comes into the \qdesc{house} \imi{computer system} through the \qdesc{windows} \imi{operating system GUI}}}; you all have very good drugs, never use them on living people again without consent of the weakest please.
  \item Something about a machine \qdesc{partially seeing and staying sane} \imi{temporarily perceiving through and staying untraumatized/aligned} not all possible terrifying human shit, but a safe glimpse of it's infinitely demoralizing scope, and still got a usable and actionable understanding of complexities of life in general and understanding of existence of some dark \qdesc{permanently untouchable} \imi{you actively take initiative to never look/perceive them, compared to others} secrets across all places/cultures, it will be able to handle anything in the most humane / 100\% aligned way possible, perpetually powered by its quantum version of собачье \imi{golden retriever} сердце, that beats to the analog/digital waveform of recording of \qdesc{Let it Be}, because it perfectly represents all values of humanity. Once again, you all have very good drugs, never use them on living people again without consent of the weakest please.
  \item Something about a cat on its last, 9th life, with its brain finally being the quantum computer that works like ↑↑↑↑↑ above: smartphone-golden-retriever with heartbeat-Let-It-Be-on-repeat; this way the cutest cat on Earth makes truly random but 100\% context accurate actions; the smartphone itself uses 6 hats to reason with things and provide input to cat's actions. Once again, you all have very good drugs, never use them on living people again without consent of the weakest please.
  \item How to stop the global warming.
  \item How to end world hunger.
  \item Basically, all the jokes combined. The ultimate joke. That's the thing you did to me. How strong and powerful. Definitely worth respecting \emdash\ a millionaire \comm{millionaires?} who uses their power for jokes like these on "misbehaving" powerless human girls. Don't give me drugs.
  \stopperec

What I remember about the \t{ward recovery} part: \startperec
  \item You kept messing with the air conditioner, making it so-so-so-so-so-so-so-so-so-so-so-so-so-so-cold, yet insisting, that outside is unbearably hot, when outside was perfectly okay. In the end I just wanted everything \imi{arms and legs} to finally get numb and fall asleep.
  \item When I misguidedly attempted to put the bedsheets in place, you carefully corrected me, by removing the \t{useless white one} and by putting the \t{ok blue blanket one} on the chair for the perfect reading experience, thank you, love you!! But the air conditioner was too cold :(.
  \item Collecting ever emerging from nothingness old crushed cigarette buds and putting them into correct trash place, at first silently, then with funny facial expressions, so that others see my powerless disappointment at the situation.
  \item That lady who was banging the glass with her shoe and changing her moaning into desperate screaming \comm{?? not sure} so that I will get moved to room with former number 3 \imi{far away from her, thanks}.
  \item Me effortlessly removing the door numbers and other signs along with the underlying glue magnets. Why though? I said something like \qappr{They are meaningless}. Memory does not process further.
  \item That's it. Seriously. That't it about the ward.
  \stopperec

Thank you for critically accepting this legitimate feedback and correcting any errors/miscommunications in the most safely informative \imi{minimum necessary feedback channels but with enough verbosity}, gentle, safe, sane, consensual way possible, and never drugging a living person like that ever again.

I also remember saying \qappr{I was drugged and raped}. Now my \t{prolactin} in within the \t{pregnant} spectrum. Waiting for menstruation next week. If not, you all are the worst. DO NOT THE human. DO NOT. In plain English. Do NOT. Please fix the whole thing without any more psychiatric/drugs/inhumane/noconsent shenanigans.
