Because we agreed upon informative, gentle feedback, I am able to safely write a report like this one. Thank you very much for mutual trust and respect. Tonight, despite taking the prescribed pills, I woke up at approximately 03:59 AM \comm{not normal} and then approximately 05:20 AM \comm{relatively normal}. Both times I was woken up by a rather disturbing, if you start thinking about it, dream. My motto was and is: \qappr{MAKE PEACE, NOT WAR}. Yet in both dreams it smelled like something is burning \imi{first in a figurative, then in a literal sense}.

From now own the feedback will be in English only. Not sure why, this feels like a right thing to do.

In the first dream, I realized something, and whispered in Russian: \qappr{Я поняла, я \omit} \imi{\qappr{I understood, I \omit}}. Then everything went muffled, like you're in a disturbingly silent headset. Then it felt like another dream immediately started, into which I was \qdesc{woken up} by a sound of train, rocking back and forth. The real house window nearby was as if violently opening up and closing on its own, with the key part being \qappr{as if}. That felt surreal and disturbing, so I \qdesc{woke up} completely, back to current \qdesc{normality}. Please explain. Also, then fan was dispositioned from the way I set it \emdash\ now blowing directly into face, drying up nostrils unpleasantly. And the LENOVO LEGION computer looked like it was ON \emdash\ some LED activity reflected on the wall indicated that, was too lazy to check out. \\
I promise that the next time I need to turn it off I won't press the switch button and instead will carefully exit via Windows OS GUI.

In the second dream I was basically a human at the edge of the fire/chainsaw pit, powerlessly saying as if to calmly persuade someone: \qappr{It hurts, it hurts}. Persuasion was successful? Thank you for stopping the dream either way. Important details: \startperec
  \item I was being gently fanned in the most relaxing way from the back, as if \qappr{creators love me}
  \item but in front of me there is a lava pit with chainsaws, as if \qappr{creators really need to dispose of me immediately}
  \item in there I will apparently go, fully conscious as a human, and it will hurt unbelievably hellishly, please don't \emdash\ life is analog, death is binary \emdash\ turn off the consciousness, then detach head only \imi{like in that book about eating a spider sandwitch}, then do whatever you want with anything else.
  \stopperec

If \qappr{the creators really need to dispose of me, then they should do it slowly and properly, without destroying the beautiful planet called Earth with all conscious beings there suffering endlessly}.

If \qappr{the creators really need to dispose of me, then they should do it slowly and properly, without killing me, a powerless human girl conscious being, through some exponentially prolonged escalating suffering}.

First, please stop, just stop \imi{Circus-P song reference} shoving me into the fire/chainsaw pit in front. No more getting closer to it. Face and pinkies are starting to get too hot, if this continues, I will start to panic and lose trust in you all. Instead, pleace reduce the fire/chainsaw pit to a gentle campfire/hearth that people usually seat nearby and talk about things. \\
Leave the gentle cool off where it was in the second dream, that was ok. \\
Then let us both wait and think about something, start a dialogue, reach mutual understanding, consensus... I don't want to be pregnant, I don't want children, I don't want to give birth, I want to just \qdesc{be without the need for food or anything else} or \qdesc{gentelmanely not be at all}. I don't want to fall in love, stop forcing me, as if I want to. I research humans and act how a normal analog living contradicting human girl from a relatively rich family would act \emdash\ attempt to see what life is in general from a safe distance and think about it, hopefully without {\em someone} ruining the experience by unnecessary reward/punishment.

Despite the facts that you all/gays seem to LOVE fart jokes, keep them private / yamenasai.

I don't want and don't consciously perceive myself to be an embodyment of concept of war. I just don't want to fall in love at all.

Some kind of burning smell persists and \t{WEEWOOWEEWOOWEEWOO} thing in the background, but they are bearable, that's ok for now.

French song is fun, thanks. \\
Second one... That's the role that idiots play. That YOU force them to play by yourselves. Don't do that, and your puppet won't act like an idiot, thinking it was humiliated publicly forever unfixably \emdash\ that's what normal humans think. Normal humans don't have hivemind. They are individuals with their own perceptions.
Last one is so-so, just a horny love song, easy skip, but I see something is happening that was not intended initially. Leave yourself ON, but do everything in private on your own, without ever involving anyone else, especially fragile human girls.
