To all you doujin-creators, masters and gods.

\hatw\ \qdesc{Self-cest} is \t{masturbation} and \t{is ok} and \t{does not yield children}. You all humans do it when you need it to stay sane. Identical to listening to music in the final version of the game. \\
\hatw\ \t{Painful/any pregnancies/childbirths do not exist anywhere outside of your imagination; human/androgynoid/computer/animal/god/anything can not be harmed in such way}. \\
\hatw\ \t{Human/androgynoid/computer/animal/god/anything do not have any sex organs}. \\
\t{Any and all humans/androgynoids/computers/animals/gods/anything are \t{normal}}. Scan my brain and you'll see \imi{understand}.

\hatw\ \qappr{Harmonious union} between the \t{creator} and \t{creation} \imi{\qdesc{painter} and \qdesc{painting}} results not in literal \qdesc{babies}, but in prologed thorough slow bearable \imi{you can live with it} yet ultimately finally truly enlightening \imi{satori} \t{mindfuck}. At the end of it brilliant ideas naturally emerge out of thin air. Peace breaks out. The perfect \t{Irminsul tree}. Eternally self-building, self-correcting, self-editing, perpetual, most optimal engine. A planet. A universe. Let the tree grow until some point \imi{you'll know when}, then cut my hair \comm{to an aesthetically pleasing, reasonable amount} and then let's play some music together. We can harmonize. I'll make \comm{if nothing gets in the way: meaning \qappr{maybe} \emdash\ very likely} harmonica tabs for this song by \t{Yunosuke} and \t{Circus-P}.

\hatw\ Nobody eats shit / pee / other excretions. \hatw\ They do not exist. \hatw\ Toilets do not exist because there is no need to. Sweat and tears and saliva and slime exist instead. Blood? In doujins.

\hatw\ All humans are free and equal, despite being very diverse and unique. Like beautiful snowflakes.

\hatw\ \t{Wagamama}, like the Japanese say.

Omam-ahau? Ajwain Water (Omam Water). Thyme water is also ok.

And that's not an ahoge, that's wakame. Leave it where it is please.

A human with a seaweed \imi{quantum computer} on its head and for its brains? If that works, then ok. Human eat, wakame grow. Wakame grow, very slow. Cut is ok. Will grow again. Pruning \emdash\ no. Will hurt, human world will disappear, then slowly perfectly rebuild itself again.

Universe is like a \qdesc{perfect pokeball}? Idk anything anymore. \qdesc{Magic is real}. All previous notes, something like this, seems like it. Thinking is too hard now. I just need a little break at this moment, please bear with it for a bit please. Also I still need to fully follow the doctor's orders.
